---
title: "Paper 2 Presentation"
author: "Aaron Mackay"
format: 
  html:
    toc: true
    embed-resources: true
execute:
  echo: false
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE}
library(AzTools)
library(tidyverse)
library(flextable)

load("objects/figs-tables.RData", envir = globalenv())
```

## Aims

1.  Explore the relationship between attitudes toward drug driving (Attitudes) and dangerous driving behaviour in people who use methamphetamine
2.  Examine how this relationship (between attitudes and dangeroud driving) is different between people who use methamphetamine and people who have never used drugs (H1: Methamphetamine Users will have stronger, positive relationships between attitudes and driving behaviour)
3.  (Bonus) Test and validate a measure of Attitude toward Drug Driving

## Method

-   Anonymous Qualitrics Survey

-   Responses from people who regularly use methamphetamine and non-drug users

### Measures

-   Dula Dangerous Driving Index (x questions)

-   Attitudes toward Drink Driving (modified for drug driving)

### Statistical Analysis

-   Multigroup Analysis using global estimation

## Results

### Descriptives

#### Sample

```{r}
#| echo: false
tbl.dems
```

#### Attitudes

```{r}
#| echo: false
plt.att.score
```

People who use methamphetamine had more favourable attitudes toward risk, more favourable peer attitudes toward drug driving and more unfavourable attitudes toward sanctions.

#### Dangerous Driving Behaviour

```{r}
#| echo: false
plt.dd.total
```

### Psychometric Properties of Questionnaire

#### Internal Consistency

```{r}
tbl.alphas
```

#### Confirmatory Factor Analysis

```{r}
tbl.cfa.loadings
```

### Analysis

#### 1. Constrained vs Free Model

**Chi Square: Free vs Constrained Model**

```{r}
#| echo: false
tbl.model.comparison
```

**Model-Wide Interactions**

```{r}
#| echo: false
tbl.model.int
```

#### 2. Examine Each Model

**Non-Drug Users**

```{r}
#| echo: false
tbl.mga.ndu
```

**Methamphetamine Users**

```{r}
#| echo: false
tbl.mga.mu
```
